Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-09-13 paper/overview.tex
Udpate bib entries

\brfcs\ integrates additional tools into OSATE to analyze, identify, and address cybersecurity vulnerabilities in the baseline AADL model (top of \figref{fig:tool-arch}).
\brfcs\ provides access to analysis tools that examine AADL models, report potential cyber vulnerabilities,
and suggest requirements for mitigation \cite{dcrypps2019,gearcase2020}.
Designers add these requirements to the \brfcs\ project requirements repository. 
A key part of the requirements management in \brfcs\ is a corresponding assurance case that provides evidence, computed directly from the model or by supporting analysis tools, showing how each requirement is satisfied.
Evidential statements must exist to address the added cyber requirements in order for \brfcs\ to build the assurance case for the project.

@@

Showing that a componest is properly implemented is accomplished through formal synthesis from the code contract.
The Semantic Properties of Language and Automata Theory (SPLAT) tool generates \emph{CakeML} code to implement the code contract.
The CakeML compiler is verified to generate binary implementations that are equivalent in semantics to the original input program \cite{cakeml}.
It proves that the resulting binary exactly preserves the meaning of the original contract to assure that the component is properly implemented.

>>>>

\brfcs\ integrates additional tools into OSATE to analyze, identify, and address cybersecurity vulnerabilities in the baseline AADL model (top of \figref{fig:tool-arch}).
\brfcs\ provides access to analysis tools that examine the model, report potential cyber vulnerabilities,
and suggest requirements for mitigation \cite{dcrypps2019,gearcase2020}.
Designers add these requirements to the \brfcs\ project requirements repository. 
A key part of the requirements management in \brfcs\ is a corresponding assurance case that provides evidence, computed directly from the model or by supporting analysis tools, showing how each requirement is satisfied.
Evidential statements must exist to address the added cyber requirements in order for \brfcs\ to build the assurance case for the project.

@@

Showing that a component is properly implemented is accomplished through formal synthesis from the code contract.
The Semantic Properties of Language and Automata Theory (SPLAT) tool generates \emph{CakeML} code to implement the code contract.
The CakeML compiler is verified to generate binary implementations that are equivalent in semantics to the original input program \cite{cakeml}.
It proves that the resulting binary exactly preserves the meaning of the original contract to assure that the component is properly implemented.
